---
title: "Read Density & Output Report (Cohort TALL)"
author: "Edward Richards"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  gbsFile:
    value: x
---
#### Dataset: Cohort_Heomnc
#### Filters: Duplicates, NA's, Qual. Score >=7

```{r setup, include=FALSE, dev="CairoPNG"}
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))
```

```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
setHook(packageEvent("grDevices", "onLoad"),
function(...) grDevices::X11.options(type='cairo'))
options(device='x11')
```

```{r,warning=FALSE,message=FALSE, echo=F, results='asis', fig.width=14, fig.height=6, fig.align = "center"}
# Load libraries and read in sequencing summary
require(ggplot2)
require(rmarkdown)
require(Cairo)
require(knitr)
require(ggplot2)
require(dplyr)
require(kableExtra)
options(scipen = 999)
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))
gbsDf <- read.delim(params$gbsFile, header = T, sep = "\t")
gbsDf <- gbsDf[!duplicated(gbsDf),]
names(gbsDf)[1] <- "Hours"
gbsDf$Hours <- as.factor(gbsDf$Hours)
NoRows <- nrow(gbsDf)
if (NoRows >= 60) {
  NoRowsHalf <- NoRows/2
  if (gbsDf[NoRows,1] == "72") {
    gbsDf1 <- gbsDf[1:NoRowsHalf-1,]
    NoRows1 <- nrow(gbsDf1) + 1
    gbsDf2 <- gbsDf[NoRows1:NoRows,]
  } else if (gbsDf[NoRows,1] == "48") {
    gbsDf1 <- gbsDf[1:NoRowsHalf-2,]
    NoRows1 <- nrow(gbsDf1) + 1
    gbsDf2 <- gbsDf[NoRows1:NoRows,]
  } else if (gbsDf[NoRows,1] == "24") {
    gbsDf1 <- gbsDf[1:NoRowsHalf-3,]
    NoRows1 <- nrow(gbsDf1) + 1
    gbsDf2 <- gbsDf[NoRows1:NoRows,]
  }
}
if (NoRows >= 60) {
  dfList <- list(gbsDf1, gbsDf2)
for (i in dfList) {
  p <- ggplot(i,aes(x = Flowcell_ID, 
                     y = Gigabases, color=Hours)) +
    geom_point() + 
    scale_color_manual(values=c('#000000','#FF0000', '#0F00FF'))+
    scale_shape_identity() +
    #To set x axis labels as vertical 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
    guides(fill=guide_legend(title="Hours"))
  print(p + coord_flip())
}
} else {
    p <- ggplot(gbsDf,aes(x = Flowcell_ID, 
                     y = Gigabases, color=Hours)) +
    geom_point() + 
    scale_color_manual(values=c('#000000','#FF0000', '#0F00FF'))+
    scale_shape_identity() +
    #To set x axis labels as vertical 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
    guides(fill=guide_legend(title="Hours"))
  print(p + coord_flip())
}
```

#### 24, 48 and 72 Hours Sequencing Stacked Barplot

```{r,warning=FALSE,message=FALSE, echo=F, results='asis', fig.width=14, fig.height=20, fig.align = "center"}
if (NoRows >= 60) {
for (i in dfList) {
  NoRows = nrow(i)
  gbsPerHourDf <- data.frame(matrix(nrow = NoRows, ncol = 3))
  colnames(gbsPerHourDf) <- colnames(i)
  gbsPerHourDf[1:NoRows,1] <- levels(i$Hours)
  gbsPerHourDf[1:NoRows,3] <- i$Flowcell_ID
  for (n in 1:(nrow(i))) {
    if (gbsPerHourDf[n,1]!="72") {
      gbsPerHourDf[n+1,2] = gbsDf[n+1,2] - gbsDf[n,2]
    } else if (gbsPerHourDf[n,1]=="72") {
      gbsPerHourDf[n-2,2] = gbsDf[n-2,2]
    }
  }
  
  pStackBar <- ggplot(gbsPerHourDf, aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="stack", stat="identity") +
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
    guides(fill=guide_legend(title="Hours"))
  
  pStackBar <- pStackBar +  scale_colour_manual(values=c('#000000','#FF0000', '#0F00FF'))
  print(pStackBar + coord_flip())
}
} else {
    NoRows = nrow(gbsDf)
  gbsPerHourDf <- data.frame(matrix(nrow = NoRows, ncol = 3))
  colnames(gbsPerHourDf) <- colnames(gbsDf)
  gbsPerHourDf[1:NoRows,1] <- levels(gbsDf$Hours)
  gbsPerHourDf[1:NoRows,3] <- gbsDf$Flowcell_ID
  for (n in 1:(nrow(gbsDf))) {
    if (gbsPerHourDf[n,1]!="72") {
      gbsPerHourDf[n+1,2] = gbsDf[n+1,2] - gbsDf[n,2]
    } else if (gbsPerHourDf[n,1]=="72") {
      gbsPerHourDf[n-2,2] = gbsDf[n-2,2]
    }
  }
  
  pStackBar <- ggplot(gbsPerHourDf, aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="stack", stat="identity") +
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
    axis.text.y = element_text(color = "grey20", size = 20, angle = 0, hjust = 1, vjust = 0, face = "bold")+
            axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain")+
    guides(fill=guide_legend(title="Hours"))
  
  pStackBar <- pStackBar +  scale_colour_manual(values=c('#000000','#FF0000', '#0F00FF'))
  print(pStackBar + coord_flip())
}
```


```{r,warning=FALSE,message=FALSE, echo=F, results='asis', fig.width=14, fig.height=20, fig.align = "center"}
if (NoRows >= 60) {
for (i in dfList) {
  pDodgeStackBar <- ggplot(i, aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="dodge", stat="identity") + 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
      guides(fill=guide_legend(title="Hours"))
  pDodgeStackBar <- pDodgeStackBar +  scale_colour_manual(values=c('#000000','#FF0000', '#0F00FF'))
#  print(pDodgeStackBar + coord_flip())
}
} else {
    pDodgeStackBar <- ggplot(gbsDf, aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="dodge", stat="identity") + 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
      guides(fill=guide_legend(title="Hours"))
  pDodgeStackBar <- pDodgeStackBar +  scale_colour_manual(values=c('#000000','#FF0000', '#0F00FF'))
 # print(pDodgeStackBar + coord_flip())
}
```

#### 24, 48 and 72 Hours Sequencing Proportionally Stacked Barplot

```{r,warning=FALSE,message=FALSE, echo=F, results='asis', fig.width=14, fig.height=20, fig.align = "center"}
if (NoRows >= 60) {
for (i in dfList) {
  NoRows = nrow(i)
  gbsPerHourDf <- data.frame(matrix(nrow = NoRows, ncol = 3))
  colnames(gbsPerHourDf) <- colnames(i)
  gbsPerHourDf[1:NoRows,1] <- levels(i$Hours)
  gbsPerHourDf[1:NoRows,3] <- i$Flowcell_ID
  for (n in 1:(nrow(i))) {
    if (gbsPerHourDf[n,1]!="72") {
      gbsPerHourDf[n+1,2] = gbsDf[n+1,2] - gbsDf[n,2]
    } else if (gbsPerHourDf[n,1]=="72") {
      gbsPerHourDf[n-2,2] = gbsDf[n-2,2]
    }
  }
  pPropStackBar <- ggplot(gbsPerHourDf,aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="fill",stat="identity") + 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
      guides(fill=guide_legend(title="Hours"))
  print(pPropStackBar + coord_flip())
}
} else {
  NoRows = nrow(gbsDf)
  gbsPerHourDf <- data.frame(matrix(nrow = NoRows, ncol = 3))
  colnames(gbsPerHourDf) <- colnames(gbsDf)
  gbsPerHourDf[1:NoRows,1] <- levels(gbsDf$Hours)
  gbsPerHourDf[1:NoRows,3] <- gbsDf$Flowcell_ID
  for (n in 1:(nrow(gbsDf))) {
    if (gbsPerHourDf[n,1]!="72") {
      gbsPerHourDf[n+1,2] = gbsDf[n+1,2] - gbsDf[n,2]
    } else if (gbsPerHourDf[n,1]=="72") {
      gbsPerHourDf[n-2,2] = gbsDf[n-2,2]
    }
  }
  pPropStackBar <- ggplot(gbsPerHourDf,aes(fill=factor(Hours,levels=c("72","48","24")), y=Gigabases, x=Flowcell_ID)) + 
    geom_bar(position="fill",stat="identity") + 
    theme(text=element_text(size=15),axis.text.x = element_text(angle = 90, 
                                     hjust = 1,
                                     vjust = 0.5,
                                     size=13,
                                     face="bold"))+
      guides(fill=guide_legend(title="Hours"))
  print(pPropStackBar + coord_flip())
}

