---
title: "Read Density & Output Report (Cohort TALL)"
author: "Edward Richards"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  seqFile:
    value: x
---
#### Dataset: 
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='asis'}
cat("####", params$seqFile, "\n")
```
#### Filters: Duplicates, NA's, Qual. Score >=7

```{r setup, include=FALSE, dev="CairoPNG"}
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))
```

```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
setHook(packageEvent("grDevices", "onLoad"),
function(...) grDevices::X11.options(type='cairo'))
options(device='x11')

# Load libraries and read in sequencing summary
require(rmarkdown)
require(Cairo)
require(knitr)
require(ggplot2)
require(scales)
require(dplyr)
require(kableExtra)
require(forcats)
require(bigreadr)
require(data.table)
library(bigreadr)
options(scipen = 999)
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))

# Filters reads below length of 1000bp
# Filters duplicate read_ids
# Filters for NA values
seqSumTab <- read.delim(params$seqFile, header = T, sep = "\t")
if(("X.1"  %in% colnames(seqSumTab))&("X" %in% colnames(seqSumTab))) {
if(!is.na(seqSumTab$X.1))
{
  seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","X.1"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    Flowcell.ID = X.1
    )
} else if (!is.na(seqSumTab$X)) {
  seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","X"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    Flowcell.ID = X
    )
} else if (!is.na(seqSumTab$Flowcell.ID)) {
  seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","Flowcell.ID"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    )
}
} else if ("X" %in% colnames(seqSumTab)) {
  if (!is.na(seqSumTab$X)) {
  seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","X"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    Flowcell.ID = X
    )
  } else if (!is.na(seqSumTab$Flowcell.ID)) {
  seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","Flowcell.ID"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    ) } else {
    seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","Flowcell.ID"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    )
  }
} else {
    seqSumTab=subset(seqSumTab, select=c("read_id", "start_time","sequence_length_template","mean_qscore_template","Flowcell.ID"))
  seqSumTab <- seqSumTab %>% 
  rename(
    read_len = sequence_length_template,
    mean_qscore = mean_qscore_template,
    )
  }
seqSumTabSubSet <-seqSumTab[which(seqSumTab[,3]>1000),]
seqSumTabSubSet <- seqSumTabSubSet[!duplicated(seqSumTabSubSet$read_id),]
seqSumTabSubSet <- na.omit(seqSumTabSubSet)
seqSumTabSubSetPass <-seqSumTabSubSet[which(seqSumTabSubSet[,4]>=7),]

# Calculate n50, total length, number of reads, average length, N90, x_border, max_len, min_len, sum_stats
read_len <- as.numeric(seqSumTabSubSetPass$read_len)
readLenList.sorted <- rev(sort(read_len))
total_length <- sum(read_len)
num_reads <- length(read_len)
avg_length <- mean(read_len)
N50 <- readLenList.sorted[cumsum(as.numeric((readLenList.sorted))) >= sum(readLenList.sorted)*0.5][1]
N90 <- readLenList.sorted[cumsum(as.numeric((readLenList.sorted))) >= sum(readLenList.sorted)*0.9][1]
x_border <- readLenList.sorted[cumsum(readLenList.sorted) >= total_length*0.001][1]
max_len <- readLenList.sorted[1]
min_len <- tail(readLenList.sorted, n = 1)
sum_stats <- c(total_length, num_reads, avg_length, N50, N90, max_len, min_len,x_border)
names(sum_stats) <- c("total_length", "num_reads", "avg_length", "N50", "N90", "max_len", "min_len",
                      "x_border")

# Make a pretty plot of read lengths
p <- ggplot(data=seqSumTabSubSetPass, aes(read_len)) + 
  geom_histogram(breaks=seq(0, sum_stats["x_border"] + 1000, by = 50), fill="blue", alpha = .4) 
x_range_max <- ggplot_build(p)$layout$panel_ranges[[1]]$x.range[2]
y_range_max <- ggplot_build(p)$layout$panel_ranges[[1]]$y.range[2]
x_text_1 <- 0.4*x_range_max
y_text_1 <- 0.6*y_range_max
title="Read Length Distribution"


p <- p + geom_vline(xintercept = sum_stats["N50"], colour="red", linetype = "dashed") +
  annotate("text", x = x_text_1, y = y_text_1, hjust = 0, size=6,
           label = sprintf("N50 = %d bp\nnum_seqs: %s\navg_len: %s bp\nmax_len = %s bp\nsum_len = %s bp", 
                           sum_stats["N50"], 
                           prettyNum(sum_stats["num_reads"], big.mark=",",scientific=FALSE),
                           prettyNum(sum_stats["avg_length"], big.mark=",",scientific=FALSE),
                           prettyNum(sum_stats["max_len"], big.mark=",",scientific=FALSE),
                           prettyNum(sum_stats["total_length"], big.mark=",",scientific=FALSE))) +
  ggtitle(title) + theme_light() +
  theme_update(plot.title = element_text(hjust = 0.5, size = 16, face="bold")) +
  labs(x="Read length (bp)", y="Counts")

# Create df for read stats
statsDf <- data.frame(matrix(nrow = 7, ncol = 1))
colnames(statsDf) <- "Values"
rownames(statsDf) <- c("Total Length", "Number of Reads", "Average Length", "N50", "N90", "Max Length", "Min. Length")
statsDf[1,1] <- total_length
statsDf[2,1] <- num_reads
statsDf[3,1] <- avg_length
statsDf[4,1] <- N50
statsDf[5,1] <- N90
statsDf[6,1] <- max_len
statsDf[7,1] <- min_len
statsDfFormatted <-apply(statsDf, 2, function(x) format(x, big.mark= ",", scientific = F))

```
### Sequencing Summary Stats
```{r echo=FALSE}
#Create table & plot with proper formatting
kable(statsDfFormatted) %>%
  kable_styling(bootstrap_options = "striped", full_width=F, position="left")
```

### Read Length Density (sorted distribution)
```{r echo=F, results='asis', out.width = "70%", fig.align = "center"}
p
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Create bin tags and values
b <- c(1, 5000,10000,15000,20000,25000,30000,35000,40000,
            45000,50000,55000,60000,65000,70000,75000,80000,85000,
            90000,95000,100000, 1000000)
tags <- c("1-5","5-10", "10-15", "15-20",
          "20-25", "25-30","30-35", "35-40",
          "40-45", "45-50","50-55","55-60", "60-65", 
          "65-70", "70-75","75-80", "80-85",
          "85-90", "90-95","95-100", "100+")
seqSumTabSubSetPass$read_len.cat <- cut(seqSumTabSubSetPass$read_len, breaks = b, labels = tags)

# Binned read density plot
binPlot <- ggplot(data=seqSumTabSubSetPass, 
                  aes(read_len.cat, fill=read_len.cat)) + 
  stat_count(width = 0.5, position = position_dodge(width=1.2)) +
  xlab("kbp") + 
  ylab("Count") + 
  ggtitle("Read Length Density") + 
  guides(fill=FALSE) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
```
### Binned Read Length Density 
```{r echo=F, results='asis', fig.width = 12, fig.align = "center", fig.asp=0.62}
binPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
#Create df & plot of total length of reads/total bps per bin
totLenBinsDf <- data.frame(matrix(nrow = 21, ncol = 2))
colnames(totLenBinsDf) <- c("Bin", "tot_len_per_bin")
tagList <- list(tags)
totLenBinsDf$Bin <- unlist(tagList)

# Calculate total length of bps within each bin and assign to df
totLenBinsDf[1,2] <- sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="1-5")])
totLenBinsDf[2,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="5-10")])
totLenBinsDf[3,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="10-15")])
totLenBinsDf[4,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="15-20")])
totLenBinsDf[5,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="20-25")])
totLenBinsDf[6,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="25-30")])
totLenBinsDf[7,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="30-35")])
totLenBinsDf[8,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="35-40")])
totLenBinsDf[9,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="40-45")])
totLenBinsDf[10,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="45-50")])
totLenBinsDf[11,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="50-55")])
totLenBinsDf[12,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="55-60")])
totLenBinsDf[13,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="60-65")])
totLenBinsDf[14,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="65-70")])
totLenBinsDf[15,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="70-75")])
totLenBinsDf[16,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="75-80")])
totLenBinsDf[17,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="80-85")])
totLenBinsDf[18,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="85-90")])
totLenBinsDf[19,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="90-95")])
totLenBinsDf[20,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="95-100")])
totLenBinsDf[21,2] <-sum(seqSumTabSubSetPass$read_len[which(seqSumTabSubSetPass$read_len.cat=="100+")])


# Binned read density plot
totLenBinsPlot <- ggplot(data=totLenBinsDf, 
                  aes(x=fct_inorder(Bin), y=tot_len_per_bin,fill=Bin)) + 
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  xlab("Bins (kbp)") + 
  ylab("bp") + 
  ggtitle("Total Length of Reads/Total bps per Bin") + 
  guides(fill=FALSE) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
```
### Total Length of Reads/Total bps per Bin
```{r echo=F, results='asis', fig.width = 12, fig.align = "center", fig.asp=0.62}
totLenBinsPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Plot log10 (x-axis) density of read lengths with N50 
pPassLog <- ggplot(seqSumTabSubSetPass, 
                   aes(x=read_len)) + 
  geom_density() + 
  scale_x_log10() + 
  ggtitle("Read Length Density (log10)") +
  xlab("Read Length") + 
  ylab("Density") +
  geom_vline(aes(xintercept=N50),
             color="blue", linetype="dashed", size=1) 
```
### Read Length Density (Log10)
```{r echo=F, results='asis', out.width = "70%", fig.align = "center"}
pPassLog
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
### Sequencing (Bps) Output Over Time
seqSumTabSubSetPassTime <- seqSumTabSubSetPass[order(seqSumTabSubSetPass$start_time),]
seqSumTabSubSetPassTime$hours <- ceiling(seqSumTabSubSetPassTime$start_time/3600)
bTime <- c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,
           19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,
           37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,
           56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73)
btags <- c("1","2", "3", "4",
          "5", "6","7", "8", "9",
          "10", "11","12","13", "14", 
          "15", "16","17", "18",
          "19", "20","21", "22", "23",
          "24", "25", "26", "27", "28",
          "29", "30", "31", "32", "33",
          "34", "35", "36", "37", "38",
          "39", "40", "41", "42", "43",
          "44", "45", "46", "47", "48",
          "49", "50", "51", "52", "53", 
          "54", "55", "56", "57", "58",
          "59", "60", "61", "62", "63",
          "64", "65", "66", "67", "68",
          "69", "70", "71", "72", "73+")
seqSumTabSubSetPassTime$hours.cat <- cut(seqSumTabSubSetPassTime$hours, breaks = bTime, labels = btags)

#Create df & plot of total length of reads/total bps per hourly bin
bpsPerHoursDf <- data.frame(matrix(nrow = 73, ncol = 2))
colnames(bpsPerHoursDf) <- c("Bin", "tot_bps_per_bin")
timeTagList <- list(btags)
bpsPerHoursDf$Bin <- unlist(timeTagList)

# Calculate total length of bps within each bin and assign to df
bpsPerHoursDf[1,2] <- sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="1")])
bpsPerHoursDf[2,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="2")])
bpsPerHoursDf[3,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="3")])
bpsPerHoursDf[4,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="4")])
bpsPerHoursDf[5,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="5")])
bpsPerHoursDf[6,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="6")])
bpsPerHoursDf[7,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="7")])
bpsPerHoursDf[8,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="8")])
bpsPerHoursDf[9,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="9")])
bpsPerHoursDf[10,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="10")])
bpsPerHoursDf[11,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="11")])
bpsPerHoursDf[12,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="12")])
bpsPerHoursDf[13,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="13")])
bpsPerHoursDf[14,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="14")])
bpsPerHoursDf[15,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="15")])
bpsPerHoursDf[16,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="16")])
bpsPerHoursDf[17,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="17")])
bpsPerHoursDf[18,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="18")])
bpsPerHoursDf[19,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="19")])
bpsPerHoursDf[20,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="20")])
bpsPerHoursDf[21,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="21")])
bpsPerHoursDf[22,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="22")])
bpsPerHoursDf[23,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="23")])
bpsPerHoursDf[24,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="24")])
bpsPerHoursDf[25,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="25")])
bpsPerHoursDf[26,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="26")])
bpsPerHoursDf[27,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="27")])
bpsPerHoursDf[28,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="28")])
bpsPerHoursDf[29,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="29")])
bpsPerHoursDf[30,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="30")])
bpsPerHoursDf[31,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="31")])
bpsPerHoursDf[32,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="32")])
bpsPerHoursDf[33,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="33")])
bpsPerHoursDf[34,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="34")])
bpsPerHoursDf[35,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="35")])
bpsPerHoursDf[36,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="36")])
bpsPerHoursDf[37,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="37")])
bpsPerHoursDf[38,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="38")])
bpsPerHoursDf[39,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="39")])
bpsPerHoursDf[40,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="40")])
bpsPerHoursDf[41,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="41")])
bpsPerHoursDf[42,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="42")])
bpsPerHoursDf[43,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="43")])
bpsPerHoursDf[44,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="44")])
bpsPerHoursDf[45,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="45")])
bpsPerHoursDf[46,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="46")])
bpsPerHoursDf[47,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="47")])
bpsPerHoursDf[48,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="48")])
bpsPerHoursDf[49,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="49")])
bpsPerHoursDf[50,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="50")])
bpsPerHoursDf[51,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="51")])
bpsPerHoursDf[52,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="52")])
bpsPerHoursDf[53,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="53")])
bpsPerHoursDf[54,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="54")])
bpsPerHoursDf[55,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="55")])
bpsPerHoursDf[56,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="56")])
bpsPerHoursDf[57,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="57")])
bpsPerHoursDf[58,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="58")])
bpsPerHoursDf[59,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="59")])
bpsPerHoursDf[60,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="60")])
bpsPerHoursDf[61,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="61")])
bpsPerHoursDf[62,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="62")])
bpsPerHoursDf[63,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="63")])
bpsPerHoursDf[64,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="64")])
bpsPerHoursDf[65,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="65")])
bpsPerHoursDf[66,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="66")])
bpsPerHoursDf[67,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="67")])
bpsPerHoursDf[68,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="68")])
bpsPerHoursDf[69,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="69")])
bpsPerHoursDf[70,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="70")])
bpsPerHoursDf[71,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="71")])
bpsPerHoursDf[72,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="72")])
bpsPerHoursDf[73,2] <-sum(seqSumTabSubSetPassTime$read_len[which(seqSumTabSubSetPassTime$hours.cat=="73+")])

# Binned read density plot
bpsPerHourPlot <- ggplot(data=bpsPerHoursDf, 
                         aes(x=fct_inorder(Bin), y=tot_bps_per_bin,fill=Bin)) +
  ggtitle("Total Length of Reads/Total bps per Bin") + 
  theme(text = element_text(size=6)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  xlab("Hours") + 
  ylab("bp") + 
  guides(fill=FALSE) 
```
### Sequencing (bps) Output Over Time
```{r echo=F, results='asis', out.width = '1800px', fig.align = "center"}
bpsPerHourPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
#Create df & plot of (ALL) total length of reads/total percentage of bps and total cumulative bps per hourly bin
percent <- function(x, digits = 2, format = "f", ...){      # Create user-defined function
  paste0(formatC(x, format = format, digits = digits, ...), "%")
}
bpsPercentHoursDf <- data.frame(matrix(nrow = 73, ncol = 3))
colnames(bpsPercentHoursDf) <- c("Bin", "Percentage_Per_Hour", "Cumulative_Percentage")
bpsPercentHoursDf$Bin <- unlist(timeTagList)
bpsPercentHoursDf[1:73,2] <- (bpsPerHoursDf[1:73,2] / total_length)*100
readSum <- 0
for(i in 1:73) {
  readSum <- bpsPercentHoursDf[i,2] + readSum
  bpsPercentHoursDf[i,3] <- readSum
}
readSum <- 0

# Percentage of total bps per binned hour
bpsPercentHoursPlot <- ggplot(data=bpsPercentHoursDf, 
                              aes(x=fct_inorder(Bin), y=Percentage_Per_Hour,fill=Bin)) +
  ggtitle("Percentage of Total bps Sequenced Within Hour") + 
  theme(text = element_text(size=6)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  xlab("Hours") + 
  ylab("Percentage") + 
  guides(fill=FALSE) 
### Sequencing (Bps) Output Over Time
```
### Percentage of bps Sequenced Per Hour 
```{r echo=F, results='asis', out.width = '1800px', fig.align = "center"}
bpsPercentHoursPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
#Create df & plot of (24/48/72) total length of reads/total percentage of bps and total cumulative bps per hourly bin
bpsPercentQuarterlyHoursDf <- data.frame(matrix(nrow = 3, ncol = 2))
colnames(bpsPercentQuarterlyHoursDf) <- c("Bin","Cumulative_Percentage")
bpsPercentQuarterlyHoursDf[1,1] <- "24"
bpsPercentQuarterlyHoursDf[2,1] <- "48"
bpsPercentQuarterlyHoursDf[3,1] <- "72"
bpsPercentQuarterlyHoursDf[1,2] <- bpsPercentHoursDf[24,3]
bpsPercentQuarterlyHoursDf[2,2] <- bpsPercentHoursDf[48,3]
bpsPercentQuarterlyHoursDf[3,2] <- bpsPercentHoursDf[72,3]

# Percentage of total bps per (24, 48, 72) binned hour
bpsPercentQuarterlyHoursPlot <- ggplot(data=bpsPercentQuarterlyHoursDf, 
                              aes(x=fct_inorder(Bin), y=Cumulative_Percentage,fill=Bin)) +
  ggtitle("Percentage of Total bps Sequenced Within Hour") + 
  theme(text = element_text(size=9)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  geom_text(aes(label = sprintf("%.2f", Cumulative_Percentage), y= Cumulative_Percentage),  vjust = 3) +
  xlab("Hours") + 
  ylab("Percentage") + 
  guides(fill=FALSE) 
```
### Percentage of bps Sequenced Per 24, 48 and 72 Hours 
```{r echo=F, results='asis', out.width = "70%", fig.align = "center"}
bpsPercentQuarterlyHoursPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Convert dfs to percentages
bpsPercentHoursDf$Percentage_Per_Hour <- lapply(bpsPercentHoursDf$Percentage_Per_Hour, round, 2)
bpsPercentHoursDf$Percentage_Per_Hour <- percent(as.numeric(bpsPercentHoursDf$Percentage_Per_Hour))
bpsPercentHoursDf$Cumulative_Percentage <- lapply(bpsPercentHoursDf$Cumulative_Percentage, round, 2)
bpsPercentHoursDf$Cumulative_Percentage <- percent(as.numeric(bpsPercentHoursDf$Cumulative_Percentage))
bpsPercentQuarterlyHoursDf$Cumulative_Percentage <- lapply(bpsPercentQuarterlyHoursDf$Cumulative_Percentage, round, 2)
bpsPercentQuarterlyHoursDf$Cumulative_Percentage <- percent(as.numeric(bpsPercentQuarterlyHoursDf$Cumulative_Percentage))
```
### Percentage of bps Sequenced Per 24, 48 and 72 Hours Table
```{r echo=FALSE}
#Create table & plot with proper formatting
kable(bpsPercentQuarterlyHoursDf) %>%
  kable_styling(bootstrap_options = "striped", full_width=F, position="left")
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Gbs per hour 
gbsPerHourDf <- data.frame(matrix(nrow = 73, ncol = 3))
colnames(gbsPerHourDf) <- c("Bin", "Gigabases", "Cumulative_Gigabases")
gbsPerHourDf$Bin <- unlist(timeTagList)
gbsPerHourDf[1:73,2] <- (bpsPerHoursDf[1:73,2] )/ 1000000000

# Total gbs per binned hour
gbsPerHourPlot <- ggplot(data=gbsPerHourDf, 
                              aes(x=fct_inorder(Bin), y=Gigabases,fill=Bin)) +
  ggtitle("Total gbs Per Hour") + 
  theme(text = element_text(size=6)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  xlab("Hours") + 
  ylab("gbs") + 
  guides(fill=FALSE) 
```
### Gbs Sequenced Per Hour
```{r echo=F, results='asis', out.width = '1800px', fig.align = "center"}
gbsPerHourPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Cumulative Gbs per hour 
gbSum <- 0
for(i in 1:73) {
  gbSum <- gbsPerHourDf[i,2] + gbSum
  gbsPerHourDf[i,3] <- gbSum
}
gbSum <- 0

# Total Cumulative gbs per binned hour
gbsPerHourPlot <- ggplot(data=gbsPerHourDf, 
                         aes(x=fct_inorder(Bin), y=Cumulative_Gigabases,fill=Bin)) +
  ggtitle("Total Cumulative gbs Per Hour") + 
  theme(text = element_text(size=6)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  xlab("Hours") + 
  ylab("gbs") + 
  guides(fill=FALSE)
```
### Total Cumulative Gbs Sequenced Per Hour
```{r echo=F, results='asis', out.width = '1800px', fig.align = "center"}
gbsPerHourPlot
```
```{r,warning=FALSE,message=FALSE, echo=FALSE, results='hide'}
# Gbs per 24, 48, 72 hours
gbsPerQuartHourDf <- data.frame(matrix(nrow = 3, ncol = 3))
colnames(gbsPerQuartHourDf) <- c("Bin", "Gigabases","Flowcell_ID")
gbsPerQuartHourDf[1,1] <- "24"
gbsPerQuartHourDf[2,1] <- "48"
gbsPerQuartHourDf[3,1] <- "72"
gbsPerQuartHourDf[1,2] <- gbsPerHourDf[24,3]
gbsPerQuartHourDf[2,2] <- gbsPerHourDf[48,3]
gbsPerQuartHourDf[3,2] <- gbsPerHourDf[72,3]
gbsPerQuartHourDf[1:3,3] <- seqSumTabSubSet$Flowcell.ID[1]

# Write 24 48 and 72 hour df to text file
write.table(gbsPerQuartHourDf,"gbsPerHour.txt",
            sep="\t",row.names=FALSE,append = TRUE)

# Percentage of total bps per (24, 48, 72) binned hour
gbsPercentQuarterlyHoursPlot <- ggplot(data=gbsPerQuartHourDf, 
                                       aes(x=fct_inorder(Bin), y=Gigabases,fill=Bin)) +
  ggtitle("Total gbs Sequenced Per 24, 48 and 72 Hours") + 
  theme(text = element_text(size=13)) +
  geom_bar(stat='identity',width = 0.5, position = position_dodge(width=0.5)) +
  geom_text(aes(label = sprintf("%.2f", Gigabases), y= Gigabases),  vjust = 3) +
  xlab("Hours") + 
  ylab("gbs") + 
  guides(fill=FALSE) 
```
### Gbs Sequenced Per 24, 48 and 72 Hours
```{r echo=F, results='asis', out.width = "70%", fig.align = "center"}
gbsPercentQuarterlyHoursPlot
```
